%-------------------------
% Resume in Latex
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Lokesh Kumar} \\ \vspace{1pt}
    \small +91 82207-34578 $|$ \href{mailto:x@x.com}{\underline{lokeshkumararun08@gmail.com}} $|$ 
    \href{https://linkedin.com/in/lokeshkumar08}{\underline{linkedin.com/lokeshkumar08}} $|$
    \href{https://github.com/DevLCodes}{\underline{github.com/DevLCodes}}
\end{center}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Engineer}{Feb 2024 -- Present}
      {Clari}{Bangalore, IN}
      \resumeItemListStart
        \resumeItem{Contributed significantly to the system architecture and implementation decisions and the development of a high-throughput ETL pipeline leveraging Kafka, Protocol Buffers, and Redis to seamlessly extract and process data from Google and Microsoft platforms. Engineered an intelligent matching service with sophisticated scoring algorithms to identify and correlate relationships between extracted data points. Orchestrated the entire data flow through Kubernetes, ensuring robust scalability and reliability from initial ingestion through final storage.}
        \resumeItem{Successfully architected and implemented a versatile data ingestion pipeline that seamlessly integrates external data sources, including Groove and other external sources with custom CRM matches, into Clari's ecosystem, enabling comprehensive activity tracking and unified analytics across multiple platforms}
        \resumeItem{Played a pivotal role in developing the time tracking of reps feature for an enterprise customer with a strict deadline. Demonstrated leadership by coordinating with cross- functional teams. This key feature was instrumental in securing a huge deal for Clari.}
        \resumeItem{Seamlessly transitioned the ownership of the Activity Loader pipeline, comprehending intricate details and nuances. Meticulously carried out migrations and optimisations to the pipeline.}

      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Engineer II}{June 2021 -- Feb 2024}
      {Clari}{Bangalore, IN}
      \resumeItemListStart
        \resumeItem{Integrated Gong and Wingman with Clari for seamless call recording access within Clari's platform. Developed embedded iframe functionality in Activity Detail View to display recorded calls, enhancing user experience.}
        \resumeItem{Implemented Territory Hierarchy with \emph{Object2Territory} model for Clari's Activity Grid, enabling support for customers operating on a territory-based model in Salesforce. Ensured accurate mapping and synchronization of territory data between Salesforce and Clari's Activity Grid.}
        \resumeItem{Led the initiative to optimize Activity queries by leveraging Activity to Opportunity association, eliminating multiple table queries. Simplified the querying process and enhanced overall efficiency.}        
        \resumeItem{Developed Activity Filters in the Opportunities module, allowing users to filter the grid based on specific criteria like \emph{"Opportunities with meetings in the last 10 days"} Provided valuable insights on high-priority opportunities.}
        \resumeItem{Revolutionized UX with the "Saved View" functionality, allowing users to save customized Account and Opportunity Grid views. Eliminated repeated filter application, streamlining workflow through, user-centric design.}

    \resumeItemListEnd

    \resumeSubheading
      {Member Technical Staff}{May 2019 -- June 2021}
      {Zoho Corporation}{Chennai, IN}
      \resumeItemListStart
        \resumeItem{Design and implementation of a scripting framework that allows users to create \emph{Custom Scripts} to automate operations within ServiceDeskPlus. Enabling users to define, execute scripts through a dedicated interface. }
        \resumeItem{Worked on migrating the core functionality of the ServiceDeskPlus application from a traditional server-side rendering approach using servlets to a modern, scalable, and lightweight architecture based on RESTful APIs.}
        
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Activity 360} $|$ \emph{Elastic Search, OpenAI, React, PostgreSQL}}{Oct 2024}
          \resumeItemListStart
            \resumeItem{Transformed Clari's traditional manual filtering system into an intuitive natural language search interface powered by OpenAI, enabling users to instantly find relevant accounts through simple conversational queries instead of navigating multiple filter combinations, Optimized system performance by implementing Elasticsearch-based querying architecture, significantly reducing grid load times while providing a more user-friendly experience for accessing and analyzing account activities across the Clari platform}
          \resumeItemListEnd
     
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Backend}{: Java, Postgres, MongoDB, JavaScript, Netflix Conductor, Redis} \\
     \textbf{Frameworks}{: SpringBoot, Liquibase} \\
     \textbf{Developer Tools}{: Git, Docker, AWS, Jenkins, JFrog, DataDog, Kubernetes, Postman, Splunk, Colima} \\
    }}
 \end{itemize}


%-------------------------------------------


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sri Krishna College of Engineering and Technology}{Coimbatore, IN}
      {Bachelor of Information Technology, CGPA: 8.1 }{Apr 2015 -- Apr 2019}
   
  \resumeSubHeadingListEnd

\end{document}
